Parsing Postfix log files

### 2008-02-24 doc/logparser.tex
Corrected logging of recipients with HELO line.

        Logging the HELO hostname in this fashion also prevents the
        complication described in \sectionref{Mail deleted before delivery
        is attempted} from occurring, because when the HELO hostname is
        logged one recipient address will be logged also.

>>>>

        Logging the HELO hostname in this fashion also prevents the
        complication described in \sectionref{Mail deleted before delivery
        is attempted} from occurring when, but only in the case where there
        is a single recipient; in that case the recipient address will be
        logged also.
